\documentclass[12pt,a4paper,oneside,notitlepage]{article}
\usepackage[a4paper, 						 
						inner=2.5cm, 
						outer=2.5cm, 
						bottom=2.6cm, 
						top=2.1cm] {geometry}

\input{../common_packages}
\input{../my_commands}

%\pagestyle{headings}
\pagestyle{plain}

\newcommand{\urlprefix}{URL~}


\begin{document}

\section*{Citations (Jan D{\v{e}}dek)}



\begin{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Fuzzy classification of web reports with linguistic text mining.
\newblock In Paolo Boldi, Giuseppe Vizzari, Gabriella Pasi, and Ricardo
  Baeza-Yates, editors, {\em Web Intelligence and Intelligent Agent Technology,
  IEEE/WIC/ACM International Conference on}, volume~3, pages 167--170, Los
  Alamitos, CA, USA, 2009. IEEE Computer Society.
\newblock ISBN 978-0-7695-3801-3.
\newblock Available from: \url{http://dx.doi.org/10.1109/WI-IAT.2009.254}.

\begin{itemize}
\item
Wei \textsc{Chen} and Parvathi \textsc{Chundi} (2011), Extracting hot spots of
  topics from time-stamped documents, \emph{Data Knowl. Eng.}, 70(7):642--660,
  \urlprefix\url{http://dx.doi.org/10.1016/j.datak.2011.03.009}.
	
\item
Jan \textsc{G{\'e}ryk}, Jaroslav \textsc{Bayer}, and Lubom{\'i}r
  \textsc{Popel{\'i}nsk{\'y}} (2011), Vyhled{\'a}v{\'a}n{\'i} a anal{\'y}za
  text{\r{u}} popisuj{\'i}c{\'i}ch v{\'y}jezdy hasi{\v{c}}sk{\'e}ho
  z{\'a}chrann{\'e}ho sboru, in Radim \textsc{Jirou{\v{s}}ek} and Vojt{\v{e}}ch
  \textsc{Sv{\'a}tek}, editors, \emph{Sborn{\'i}k
  p{\v{r}}{\'i}sp{\v{e}}vk{\r{u}} 10. ro{\v{c}}n{\'i}ku konference ZNALOSTI},
  pp. 21--32, ISBN 978-80-248-2369-0,
  \urlprefix\url{http://is.muni.cz/th/72902/fi_r/znalosti2011_firemen.pdf}.	
	
%\item
%Ivo \textsc{La\v{s}ek} and Peter \textsc{Vojt{\'a}\v{s}} (2011), Semantic
  %Information Filtering - Beyond Collaborative Filtering, in \emph{Proceedings
  %of the 4th International Semantic Search Workshop of the 20th Int. World Wide
  %Web Conference {WWW2011}}, Hyderabad, India,
  %\urlprefix\url{http://research.i-lasek.cz/_media/publications/semsearch11_lasek.pdf}.
%
%\item
%Peter \textsc{Vojt{\'a}{\v{s}}} (2010), Information technologies-synergy of
  %theory and application?, in \emph{ITAT 2010 Information Technologies --
  %Applications and Theory}, pp. 7--8, {PONT} s. r. o., Se{\v{n}}a, Slovakia,
  %ISBN 978-80-970179-4-1,
  %\urlprefix\url{http://ceur-ws.org/Vol-683/paper2.pdf}.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\item
Jan D{\v{e}}dek, Peter Vojt{\'{a}}{\v{s}}, and Marta Vomlelov{\'{a}}.
\newblock Fuzzy {ILP} classification of web reports after linguistic text
  mining.
\newblock {\em Information Processing \& Management}, 48\penalty0 (3):\penalty0
  438 -- 450, 2012.
\newblock Soft Approaches to IA on the Web.
\newblock Available from:
  \url{http://www.sciencedirect.com/science/article/pii/S0306457311000264}.

\begin{itemize}
\item
Miguel \textsc{Del-Fresno~Garc\'{\i}a} (2011), Infosociabilidad:
  monitorizaci\'{o}n e investigaci\'{o}n en la web 2.0 para la toma de
  decisiones., \emph{El profesional de la informaci\'{o}n}, 20(5):548--554,
  \urlprefix\url{http://eprints.rclis.org/bitstream/10760/16150/1/Miguel-Del-Fresno-Infosociabilidad-reputacion-Online.pdf}.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Linguistic extraction for semantic annotation.
\newblock In Costin Badica, Giuseppe Mangioni, Vincenza Carchiolo, and Dumitru
  Burdescu, editors, {\em 2nd International Symposium on Intelligent
  Distributed Computing}, volume 162 of {\em Studies in Computational
  Intelligence}, pages 85--94, Catania, Italy, 2008. Springer-Verlag.
\newblock ISBN 978-3-540-85256-8.
\newblock Available from:
  \url{http://www.springerlink.com/content/w7213j007t416132}.


\begin{itemize}
\item
Ivo \textsc{La\v{s}ek} (2011), News Information Filtering Supported by Semantic
  Web Knowledge Base, in \emph{{Proceedings of 15th International Student
  Conference on Electrical Engineering POSTER 2011 (CDROM)}}, pp. 1--5, Faculty
  of Electrical Engineering, Czech Technical University in Prague, Prague, ISBN 978-80-01-04806-1,
  \urlprefix\url{http://research.i-lasek.cz/_media/publications/poster2011_lasek.pdf}.

%\item
%Ivo \textsc{La\v{s}ek} and Peter \textsc{Vojt{\'a}\v{s}} (2011), Semantic
  %Information Filtering - Beyond Collaborative Filtering, in \emph{Proceedings
  %of the 4th International Semantic Search Workshop of the 20th Int. World Wide
  %Web Conference {WWW2011}}, Hyderabad, India,
  %\urlprefix\url{http://research.i-lasek.cz/_media/publications/semsearch11_lasek.pdf}.	

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item
Jan D{\v{e}}dek, Alan Eckhardt, Leo Galambo{\v{s}}, and Peter
  Vojt{\'{a}}{\v{s}}.
\newblock Discussion on uncertainty ontology for annotation and reasoning (a
  position paper).
\newblock In P.~C.~G. da~Costa, editor, {\em {URSW} '08 Uncertainty Reasoning
  for the Semantic Web - Volume 4}, volume 423 of {\em {CEUR} Workshop
  Proceedings}, pages 128--129. The 7th International Semantic Web Conference,
  2008.
\newblock Available from:
  \url{http://c4i.gmu.edu/ursw/2008/papers/URSW2008_P2_DedekEtAl.pdf}.

\begin{itemize}
\item
Laurie \textsc{Serrano}, Maroua \textsc{Bouzid}, Thierry \textsc{Charnois}, and
  Bruno \textsc{Grilheres} (2012), Vers un syst{\`e}me de capitalisation des
  connaissances: extraction d'{\'e}v{\'e}nements par combinaison de plusieurs
  approches., in \emph{{Workshop SOS-DLWD'2012: From Open Sources to Web of
  Data, at EGC'2012}}, pp. 49--61, Bordeaux,
  \urlprefix\url{https://www.greyc.fr/sites/default/files/users/serranol/Extraction_d_evenements_par_combinaison_de_plusieurs_approches.pdf}.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\item
Jan D{\v{e}}dek.
\newblock Extraction of semantic information from web resources.
\newblock In Jana {\v{S}}afr{\'{a}}nkov{\'{a}} and Ji{\v{r}}{\'{i}}
  Pavl{\r{u}}, editors, {\em {WDS}'08 Proceedings of Contributed Papers: Part I
  - Mathematics and Computer Sciences}, pages 224--229, Praha, 2008.
  Matfyzpress.
\newblock ISBN 978-80-7378-065-4.
\newblock Available from:
  \url{http://www.mff.cuni.cz/veda/konference/wds/proc/pdf08/WDS08_138_i2_Dedek.pdf}.

\begin{itemize}
\item
Hejab Ma'azer~Khaled \textsc{Al-fawareh} (2010), \emph{Resolving Ambiguity in
  Entity and Fact Extraction Through a Hybrid Approach}, Ph.D. thesis,
  Universiti Utara Malaysia, \urlprefix\url{http://etd.uum.edu.my/2401/}.
\end{itemize}


\end{itemize}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


