\documentclass[12pt,a4paper,oneside,notitlepage]{article}
\usepackage[a4paper, 						 
						inner=2.5cm, 
						outer=2.5cm, 
						bottom=2.6cm, 
						top=2.1cm] {geometry}

\input{../common_packages}
\input{../my_commands}

%\pagestyle{headings}
\pagestyle{plain}

\newcommand{\urlprefix}{URL~}


\begin{document}

\section*{Publications (Jan D{\v{e}}dek)}


\subsection*{Refereed (English)}

\begin{itemize}


\item
Jan D{\v{e}}dek, Peter Vojt{\'{a}}{\v{s}}, and Marta Vomlelov{\'{a}}.
\newblock Fuzzy {ILP} classification of web reports after linguistic text
  mining.
\newblock {\em Information Processing \& Management}, 48\penalty0 (3):\penalty0
  438 -- 450, 2012.
\newblock Soft Approaches to IA on the Web.
\newblock Available from:
  \url{http://www.sciencedirect.com/science/article/pii/S0306457311000264}.


\item
Jan D{\v{e}}dek.
\newblock Towards semantic annotation supported by dependency linguistics and
  {ILP}.
\newblock In {\em Proceedings of the 9th International Semantic Web Conference
  (ISWC2010), Part II}, volume 6497 of {\em Lecture Notes in Computer Science},
  pages 297--304, Shanghai / China, 2010. Springer-Verlag Berlin Heidelberg.
\newblock ISBN 978-3-642-17748-4.
\newblock Available from:
  \url{http://iswc2010.semanticweb.org/accepted-papers/219}.

\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Semantic annotation semantically: Using a shareable extraction
  ontology and a reasoner.
\newblock In Pascal Lorenz and Eckhard Ammann, editors, {\em {SEMAPRO 2011},
  The Fifth International Conference on Advances in Semantic Processing}, pages
  29--34. (c) {IARIA}, {XPS}, 2011.
\newblock ISBN 978-1-61208-175-5.
\newblock Available from:
  \url{http://www.thinkmind.org/index.php?view=article&articleid=semapro_2011_2_10_50013}.



\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Linguistic extraction for semantic annotation.
\newblock In Costin Badica, Giuseppe Mangioni, Vincenza Carchiolo, and Dumitru
  Burdescu, editors, {\em 2nd International Symposium on Intelligent
  Distributed Computing}, volume 162 of {\em Studies in Computational
  Intelligence}, pages 85--94, Catania, Italy, 2008. Springer-Verlag.
\newblock ISBN 978-3-540-85256-8.
\newblock Available from:
  \url{http://www.springerlink.com/content/w7213j007t416132}.


\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Computing aggregations from linguistic web resources: a case study in
  czech republic sector/traffic accidents.
\newblock In Cosmin Dini, editor, {\em Second International Conference on
  Advanced Engineering Computing and Applications in Sciences}, pages 7--12.
  {IEEE} Computer Society, 2008.
\newblock ISBN 978-0-7695-3369-8.
\newblock Available from: \url{http://dx.doi.org/10.1109/ADVCOMP.2008.17}.

\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Exploitation of linguistic tools in semantic extraction - a design.
\newblock In Mieczys{{\l}}aw K{{\l}}opotek, Adam Przepi{\'{o}}rkowski,
  S{{\l}}awomir Wierzcho{\'{n}}, and Krzysztof Trojanowski, editors, {\em
  Intelligent Information Systems {XVI}}, pages 239--247, Zakopane, Poland,
  2008. Academic Publishing House {EXIT}.
\newblock ISBN 978-83-60434-44-4.
\newblock Available from:
  \url{http://iis.ipipan.waw.pl/2008/proceedings/iis08-23.pdf}.


\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Fuzzy classification of web reports with linguistic text mining.
\newblock In Paolo Boldi, Giuseppe Vizzari, Gabriella Pasi, and Ricardo
  Baeza-Yates, editors, {\em Web Intelligence and Intelligent Agent Technology,
  IEEE/WIC/ACM International Conference on}, volume~3, pages 167--170, Los
  Alamitos, CA, USA, 2009. IEEE Computer Society.
\newblock ISBN 978-0-7695-3801-3.
\newblock Available from: \url{http://dx.doi.org/10.1109/WI-IAT.2009.254}.


\item
Jan D{\v{e}}dek, Alan Eckhardt, and Peter Vojt{\'{a}}{\v{s}}.
\newblock Experiments with czech linguistic data and {ILP}.
\newblock In Filip {\v{Z}}elezn{\'{y}} and Nada Lavra{\v{c}}, editors, {\em
  {ILP} 2008 - Inductive Logic Programming (Late Breaking Papers)}, pages
  20--25, Prague, Czech Republic, 2008. Action M.
\newblock ISBN 978-80-86742-26-7.
\newblock Available from:
  \url{http://ida.felk.cvut.cz/ilp2008/ILP08_Late_Breaking_Papers.pdf}.




\item
Jan D{\v{e}}dek, Alan Eckhardt, Leo Galambo{\v{s}}, and Peter
  Vojt{\'{a}}{\v{s}}.
\newblock Discussion on uncertainty ontology for annotation and reasoning (a
  position paper).
\newblock In P.~C.~G. da~Costa, editor, {\em {URSW} '08 Uncertainty Reasoning
  for the Semantic Web - Volume 4}, volume 423 of {\em {CEUR} Workshop
  Proceedings}, pages 128--129. The 7th International Semantic Web Conference,
  2008.
\newblock Available from:
  \url{http://c4i.gmu.edu/ursw/2008/papers/URSW2008_P2_DedekEtAl.pdf}.


\item
Jan D{\v{e}}dek.
\newblock Web information extraction systems for web semantization.
\newblock In Peter Vojt{\'{a}}{\v{s}}, editor, {\em {ITAT} 2009 Information
  Technologies - Applications and Theory}, pages 1--6, Se{\v{n}}a, Slovakia,
  2009. {PONT} Slovakia.
\newblock ISBN 978-80-970179-2-7.
\newblock Available from: \url{http://ceur-ws.org/Vol-584/paper1.pdf}.


\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Web information extraction for e-environment.
\newblock In Jiri Hrebicek, Jiri Hradec, Emil Pelikan, Ondrej Mirovsky, Werner
  Pillmann, Ivan Holoubek, and Thomas Bandholtz, editors, {\em Proceedings of
  the European conference of the Czech Presidency of the Council of the {EU
  TOWARDS eENVIRONMENT}}, pages 138--143, Brno, Czech Republic, 2009. Masaryk
  University.
\newblock ISBN 978-80-210-4824-9.
\newblock Available from: \url{http://www.e-envi2009.org/?proceedings}.







\end{itemize}

\subsection*{Refereed (Czech and Slovak)}

\begin{itemize}





\item
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Extrakce informac{\'{i}} z textov{\v{e}} orientovan{\'{y}}ch
  zdrojù webu.
\newblock In V{\'{a}}clav Sn{\'{a}}{\v{s}}el, editor, {\em Znalosti 2008},
  pages 331--334, 2008.
\newblock ISBN 978-80-227-2827-0.
\newblock Available from:
  \url{http://znalosti2008.fiit.stuba.sk/download/articles/znalosti2008-Dedek.pdf}.


\item
Jan D{\v{e}}dek, Peter Vojt{\'{a}}{\v{s}}, and Marta Vomlelov{\'{a}}.
\newblock Evaluace fuzzy {ILP} klasifik{\'{a}}toru na datech o dopravn{\'{i}}ch
  nehod{\'{a}}ch.
\newblock In Pavel Smr{\v{z}}, editor, {\em Znalosti 2010}, pages 187--190,
  Jind{\v{r}}ichùv Hradec, 2010. V{\v{S}}E v Praze, Oeconomica.
\newblock ISBN 978-80-245-1636-3.



\item
Jan D{\v{e}}dek, Peter Vojt{\'{a}}{\v{s}}, and Juraj Vojt{\'{a}}{\v{s}}.
\newblock Obsahuje web indikace bl\'{i}\v{z}\'{i}c\'{i} se krize? {U}m\'{i}me
  je rozeznat?
\newblock In Ji\v{r}\'{i} Vo\v{r}\'{i}\v{s}ek, editor, {\em Syst\'{e}mov\'{a}
  integrace 2010}, pages 166--175, Praha, 2010. V{\v{S}}E v Praze, Oeconomica.
\newblock ISBN 978-80-245-1660-8.


\end{itemize}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


