%\chapter{Listings}
\newapendix{Listings}{sec:listings}

Individual listings are placed as separate sections on following pages.

\clearpage
\section{Sample of Czech WordNet}	\label{sec:listing_czWordNet}
This sample shows the word coverage in the domain of means of transport and vehicles. We do not provide the complete transcript of Czech words. The top subtree demonstrates the distance between the words ``autobus, autokar'' (bus, coach) and ``kamion'' (truck) in the hypernym hierarchy and the rest of the sample lists all hyponyms of the three selected words: ``motorové vozidlo'' (motor vehicle), ``nákladní automobil'' (truck) and ``auto, vůz'' (car).

\bigskip

\noindent\fbox{\hspace{3mm}\parbox[b]{0.965\hsize}{
\hspace*{0cm}$\bullet$ entita:1\\
\hspace*{1cm}$\bullet$ objekt:1\\
\hspace*{2cm}$\bullet$ celek:1\\
\hspace*{3cm}$\bullet$ artefakt:1, výtvor:2, výrobek:2\\
\hspace*{4cm}$\bullet$ vybavení:2\\
\hspace*{5cm}$\bullet$ přepravní prostředek:1, transportní prostředek:1\\
\hspace*{6cm}$\triangleright$ \textbf{veřejná doprava:1}\\
\hspace*{7cm}$\Rightarrow$ \emph{autobus:1, autokar:1}\\
\hspace*{6cm}$\triangleright$ \textbf{dopravní prostředek:1}\\
\hspace*{7cm}$\bullet$ kolové vozidlo:1\\
\hspace*{8cm}$\bullet$ samohybné vozidlo:1,\\
\hspace*{8cm}\phantom{$\bullet$} vozidlo s vlastním pohonem:1\\
\hspace*{9cm}$\bullet$ motorové vozidlo:1\\
\hspace*{10cm}$\bullet$ nákladní automobil:1\\
\hspace*{11cm}$\Rightarrow$ \emph{kamion:1}

\vspace{0.5cm}

\setlength{\columnsep}{0cm}

\begin{multicols}{2}

\hspace*{0cm}$\bullet$ motorové vozidlo:1\\
\hspace*{1cm}$\bullet$ motocykl:1\\
\hspace*{1cm}$\bullet$ nákladní automobil:1\\
\hspace*{1cm}$\bullet$ obojživelné vozidlo:1\\
\hspace*{1cm}$\bullet$ auto:1, vůz:2\\
\hspace*{1cm}$\bullet$ pohřební vůz:1\\
\hspace*{1cm}$\bullet$ sněžný pluh:1, pluh:2\\
\hspace*{1cm}$\bullet$ golfový vozík:1\\

\vspace{0.5cm}

\hspace*{0cm}$\bullet$ nákladní automobil:1\\
\hspace*{1cm}$\bullet$ dodávka:3\\
\hspace*{1cm}$\bullet$ sklápěč:1,\\
\hspace*{1cm}\phantom{$\bullet$}  vyklápěcí nákladní automobil:1\\
\hspace*{1cm}$\bullet$ tahač:1\\
\hspace*{1cm}$\bullet$ pick-up:1,\\
\hspace*{1cm}\phantom{$\bullet$} malý nákladní automobil:1\\
\hspace*{1cm}$\bullet$ hasící vůz:1, požární stříkačka:1\\
\hspace*{1cm}$\bullet$ rozhlasový vůz:1\\
\hspace*{1cm}$\bullet$ kamion:1\\
\hspace*{1cm}$\bullet$ nákladní automobil s přívěsem:1\\
\hspace*{1cm}$\bullet$ popelářský vůz:1, popelářské auto:1,\\
\hspace*{1cm}\phantom{$\bullet$} bobr:3\\

\columnbreak

\hspace*{0cm}$\bullet$ auto:1, vůz:2\\
\hspace*{1cm}$\bullet$ limuzína:1\\
\hspace*{1cm}$\bullet$ elektrický vozík:1\\
\hspace*{1cm}$\bullet$ závodní vůz:1,\\
\hspace*{1cm}\phantom{$\bullet$} závodní automobil:1\\
\hspace*{1cm}$\bullet$ sportovní vůz:1\\
\hspace*{1cm}$\bullet$ kabriolet:1, sporťák:1\\
\hspace*{1cm}$\bullet$ vrak:3\\
\hspace*{1cm}$\bullet$ limuzína:2\\
\hspace*{1cm}$\bullet$ hlídkový vůz:1,\\
\hspace*{1cm}\phantom{$\bullet$} policejní vůz:1\\
\hspace*{1cm}$\bullet$ sériový automobil:1\\
\hspace*{1cm}$\bullet$ cestovní vůz:1\\
\hspace*{1cm}$\bullet$ džíp:1\\
\hspace*{1cm}$\bullet$ kupé:1\\
\hspace*{1cm}$\bullet$ kabriolet:3\\
\hspace*{1cm}$\bullet$ kombi:1\\
\hspace*{1cm}$\bullet$ taxi:1\\
\hspace*{1cm}$\bullet$ ambulance:1, sanitka:1,\\
\hspace*{1cm}\phantom{$\bullet$} pohotovost:6, záchranka:1,\\
\hspace*{1cm}\phantom{$\bullet$} sanita:1\\
\end{multicols}
%\setlength{\columnsep}{5cm}
}}


\clearpage
\section{Extraction Rules Export to OWL in Prolog.} \label{sec:onto_prolog_rules_export_module}
\begin{minted}[linenos,  fontsize=\footnotesize,
               frame=lines, tabsize=2]{prolog}
serialize_rule_file(RuleFileName, OutputFileName, OntologyURI, ObjectProperties) :-
	assert(objectProperties(ObjectProperties)),
	open(OutputFileName, 'write', Stream), set_output(Stream),
	write('<?xml version="1.0" encoding="UTF-8"?>\n'),
	write('<!DOCTYPE Ontology [ <!ENTITY xsd "http://www.w3.org/2001/XMLSchema#" >\n'),
	write('	<!ENTITY pml "http://ufal.mff.cuni.cz/pdt/pml/" > ]>\n'),		
	write('<Ontology xmlns="http://www.w3.org/2002/07/owl#"\n'),	
	format('	ontologyIRI="~a">\n',[OntologyURI]),
	consult(RuleFileName), %Each rule in the file will be processed by serialize_rule,
	                       %because of the term_expansion setting on the last line. 	                         
	write('</Ontology>'),			
	close(Stream).

serialize_rule(:-(H, B)) :- 	
	numbervars(:-(H, B), 0, _),	
	write('<DLSafeRule>\n'),		
		write('<Body>\n'),          
			serialize_term(B),                       %Rule body
		write('\n</Body>\n'), write('<Head>\n'),
			serialize_term(H),                       %Rule head
		write('\n</Head>\n'),			
	write('</DLSafeRule>\n\n'),!.
	 
%Serialize object property
serialize_term(T):- functor(T,F,N), objectProperties(OProps), member(F, OProps),!,	
	write('<ObjectPropertyAtom>'),
	format('<ObjectProperty IRI="&pml;~a"/>\n', [F]),
	serialize_arg(T, 0, N),		
	write('</ObjectPropertyAtom>').

%Serialize datatype property
serialize_term(T):- functor(T,F,N),	
	write('<DataPropertyAtom>'),
	format('<DataProperty IRI="&pml;~a"/>\n', [F]),
	serialize_arg(T, 0, N),		
	write('</DataPropertyAtom>').

%Serialize argument list
serialize_term(','(A,B)):- serialize_term(A), write('\n'), serialize_term(B),!.

%Serialize variable
serialize_term('$VAR'(N)):- char_code('a',I), Var is I + N,
	format('<Variable IRI="urn:swrl#~c"/>\n',[Var]),!.
%Serialize simple atom or string (printed without quotes)
serialize_term(T):- atom(T), format('<Literal>~a</Literal>\n',[T]),!.
%Serialize number
serialize_term(T):- simple(T), format('<Literal>~k</Literal>\n',[T]),!.

%Serialize term arguments: serialize_arg(+Term, +CurrentArgNumber, +LastArgNumber)
serialize_arg(T, _, 0).
serialize_arg(T, N, N).
serialize_arg(T, M, N) :-  M2 is M+1, arg(M2, T, A),
	serialize_term(A), serialize_arg(T, M2, N).  
                                               %All predicates loaded by consult
term_expansion(T,T):- serialize_rule(T).       %will be processed by serialize_rule.
\end{minted}