\begin{thebibliography}{10}

\bibitem{biblio:ArtEquAKT}
Harith Alani, Sanghee Kim, David~E. Millard, Mark~J. Weal, Wendy Hall, Paul~H.
  Lewis, and Nigel~R. Shadbolt.
\newblock Automatic ontology-based knowledge extraction from web documents.
\newblock {\em IEEE Intelligent Systems}, 18:14--21, 2003.

\bibitem{biblio:Appelt-Israel}
Douglas~E. Appelt and David~J. Israel.
\newblock Introduction to information extraction technology.
\newblock A tutorial prepared for {IJCAI-99}, Stockholm, Schweden, 1999.

\bibitem{biblio:LeeWebThings}
Tim Berners-Lee.
\newblock The web of things.
\newblock {\em ERCIM News - Special: The Future Web}, 72:3, January 2008.

\bibitem{biblio:2001-Berners-Lee-SemanticWeb}
Tim Berners-Lee, James Hendler, and Ora Lassila.
\newblock The semantic web, a new form of web content that is meaningful to
  computers will unleash a revolution of new possibilities.
\newblock {\em Scientific American}, 284(5):34--43, May 2001.

\bibitem{biblio:SOBA}
Paul Buitelaar, Philipp Cimiano, Anette Frank, Matthias Hartung, and Stefania
  Racioppa.
\newblock Ontology-based information extraction and integration from
  heterogeneous data sources.
\newblock {\em Int. J. Hum.-Comput. Stud.}, 66(11):759--788, 2008.

\bibitem{biblio:Chang2006}
Chia-Hui Chang, M.~Kayed, M.~R. Girgis, and K.~F. Shaalan.
\newblock A survey of web information extraction systems.
\newblock {\em Knowledge and Data Engineering, IEEE Transactions on},
  18(10):1411--1428, 2006.

\bibitem{biblio:SelfAnnotWeb}
Philipp Cimiano, Siegfried Handschuh, and Steffen Staab.
\newblock Towards the self-annotating web.
\newblock In {\em WWW '04: Proceedings of the 13th international conference on
  World Wide Web}, pages 462--471, New York, NY, USA, 2004. ACM.

\bibitem{biblio:DeEcExperimentswith2008}
Jan D{\v{e}}dek, Alan Eckhardt, and Peter Vojt{\'{a}}{\v{s}}.
\newblock Experiments with czech linguistic data and {ILP}.
\newblock In Filip {\v{Z}}elezn{\'{y}} and Nada Lavra{\v{c}}, editors, {\em
  {ILP} 2008 - Inductive Logic Programming (Late Breaking Papers)}, pages
  20--25, Prague, Czech Republic, 2008. Action M.

\bibitem{biblio:DeEcSemantickyWeb2008}
Jan D{\v{e}}dek, Alan Eckhardt, Peter Vojt{\'{a}}{\v{s}}, and Leo
  Galambo{\v{s}}.
\newblock S{\'{e}}mantick{\'{y}} web.
\newblock In V{\'{a}}clav {\v{R}}epa and Oleg Svato{\v{s}}, editors, {\em
  {DATAKON} 2008}, pages 12--30, Brno, 2008.

\bibitem{biblio:DeVoComputingaggregations2008}
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Computing aggregations from linguistic web resources: a case study in
  czech republic sector/traffic accidents.
\newblock In Cosmin Dini, editor, {\em Second International Conference on
  Advanced Engineering Computing and Applications in Sciences}, pages 7--12.
  {IEEE} Computer Society, 2008.

\bibitem{biblio:DeVoExploitationlinguistic2008}
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Exploitation of linguistic tools in semantic extraction - a design.
\newblock In Mieczyslaw Klopotek, Adam Przepi{\'{o}}rkowski, Slawomir
  Wierzcho{\'{n}}, and Krzysztof Trojanowski, editors, {\em Intelligent
  Information Systems {XVI}}, pages 239--247, Zakopane, Poland, 2008. Academic
  Publishing House {EXIT}.

\bibitem{biblio:DeVoLinguisticextraction2008}
Jan D{\v{e}}dek and Peter Vojt{\'{a}}{\v{s}}.
\newblock Linguistic extraction for semantic annotation.
\newblock In Costin Badica, Giuseppe Mangioni, Vincenza Carchiolo, and Dumitru
  Burdescu, editors, {\em 2nd International Symposium on Intelligent
  Distributed Computing}, volume 162 of {\em Studies in Computational
  Intelligence}, pages 85--94, Catania, Italy, 2008. Springer-Verlag.

\bibitem{biblio:seekerIBM}
Stephen Dill, Nadav Eiron, David Gibson, Daniel Gruhl, R.~Guha, Anant Jhingran,
  Tapas Kanungo, Sridhar Rajagopalan, Andrew Tomkins, John~A. Tomlin, and
  Jason~Y. Zien.
\newblock Semtag and seeker: bootstrapping the semantic web via automated
  semantic annotation.
\newblock In {\em WWW '03: Proceedings of the 12th international conference on
  World Wide Web}, pages 178--186, New York, NY, USA, 2003. ACM.

\bibitem{biblio:EcHoUncertaintyIssues2008}
Alan Eckhardt, T.~Horv{\'{a}}th, D.~Maru{\v{s}}{\v{c}}{\'{a}}k,
  R.~Novotn{\'{y}}, and Peter Vojt{\'{a}}{\v{s}}.
\newblock {\em Uncertainty Issues and Algorithms in Automating Process
  Connecting Web and User}, volume 5327 of {\em Lecture Notes in Computer
  Science}.
\newblock Springer Verlag, 2008.

\bibitem{biblio:MUC6}
Ralph Grishman and Beth Sundheim.
\newblock Message understanding conference-6: a brief history.
\newblock In {\em Proceedings of the 16th conference on Computational
  linguistics}, pages 466--471, Morristown, NJ, USA, 1996. Association for
  Computational Linguistics.

\bibitem{biblio:Horrocks_Onto}
Ian Horrocks.
\newblock Ontologies and the semantic web.
\newblock {\em Commun. ACM}, 51(12):58--67, 2008.

\bibitem{biblio:extraction_detail_pages}
Kristina Lerman, Lise Getoor, Steven Minton, and Craig Knoblock.
\newblock Using the structure of web sites for automatic segmentation of
  tables.
\newblock In {\em SIGMOD '04: Proceedings of the 2004 ACM SIGMOD international
  conference on Management of data}, pages 119--130, New York, NY, USA, 2004.
  ACM.

\bibitem{biblio:WebDataMining}
Bing Liu.
\newblock {\em Web Data Mining}.
\newblock Springer-Verlag, 2007.

\bibitem{biblio:tables}
David Pinto, Andrew Mccallum, Xing Wei, and Bruce~W. Croft.
\newblock Table extraction using conditional random fields.
\newblock In {\em SIGIR '03: Proceedings of the 26th annual international ACM
  SIGIR conference on Research and development in informaion retrieval}, pages
  235--242, New York, NY, USA, 2003. ACM Press.

\bibitem{biblio:KIM}
Borislav Popov, Atanas Kiryakov, Damyan Ognyanoff, Dimitar Manov, and Angel
  Kirilov.
\newblock Kim -- a semantic platform for information extraction and retrieval.
\newblock {\em Nat. Lang. Eng.}, 10(3-4):375--392, 2004.

\bibitem{biblio:repetitons}
Hongkun Zhao, Weiyi Meng, Zonghuan Wu, Vijay Raghavan, and Clement Yu.
\newblock Fully automatic wrapper generation for search engines.
\newblock In {\em WWW Conference}, pages 66--75, 2005.

\end{thebibliography}
