\begin{thebibliography}{10}

\bibitem{Dedek:FuzzWI}
J.~D\v{e}dek and P.~Vojt{\'a}\v{s}, ``Fuzzy classification of web reports with
  linguistic text mining,'' in {\em Web Intelligence/IAT Workshops, Soft
  approaches to information access on the Web}, (Milan, Italy), Accepted for
  publication, 2009.

\bibitem{dedek:PDT20_CD}
J.~Haji{\v{c}}, E.~Haji{\v{c}}ov{\'{a}}, J.~Hlav{\'{a}}{\v{c}}ov{\'{a}},
  V.~Klime\v{s}, J.~M\'{i}rovsk\'{y}, P.~Pajas, J.~{\v{S}}t{\v{e}}p{\'{a}}nek,
  B.~Vidov{\'{a}}-Hladk{\'{a}}, and Z.~{\v{Z}}abokrtsk{\'{y}}, ``Prague
  dependency treebank 2.0 cd--rom.'' Linguistic Data Consortium LDC2006T01,
  Philadelphia 2006, 2006.

\bibitem{dedek:KlTransformationBasedTectogrammatical2006}
V.~Klime\v{s}, ``Transformation-based tectogrammatical analysis of czech,'' in
  {\em Proceedings of the 9th International Conference, {TSD} 2006}, no.~4188
  in Lecture Notes In Computer Science, pp.~135--142, Springer-Verlag Berlin
  Heidelberg, 2006.

\bibitem{dedek:MiBeAnnotationtectogrammatical2006}
M.~Mikulov\'{a}, A.~B\'{e}mov\'{a}, J.~Haji\v{c}, E.~Haji\v{c}ov\'{a},
  J.~Havelka, V.~Kol\'{a}\v{r}ov\'{a}, L.~Ku\v{c}ov\'{a}, M.~Lopatkov\'{a},
  P.~Pajas, J.~Panevov\'{a}, M.~Raz\'{i}mov\'{a}, P.~Sgall,
  J.~\v{S}t\v{e}p\'{a}nek, Z.~Ure\v{s}ov\'{a}, K.~Vesel\'{a}, and
  Z.~\v{Z}abokrtsk\'{y}, ``Annotation on the tectogrammatical level in the
  prague dependency treebank. annotation manual,'' Tech. Rep.~30, \'{U}{FAL}
  {MFF} {UK}, Prague, Czech Rep., 2006.

\bibitem{dedek:DeVoLinguisticextraction2008}
J.~D{\v{e}}dek and P.~Vojt{\'{a}}{\v{s}}, ``Linguistic extraction for semantic
  annotation,'' in {\em 2nd International Symposium on Intelligent Distributed
  Computing} (C.~Badica, G.~Mangioni, V.~Carchiolo, and D.~Burdescu, eds.),
  vol.~162 of {\em Studies in Computational Intelligence}, (Catania, Italy),
  pp.~85--94, Springer-Verlag, 2008.

\bibitem{dedek:DeVoComputingaggregations2008}
J.~D{\v{e}}dek and P.~Vojt{\'{a}}{\v{s}}, ``Computing aggregations from
  linguistic web resources: a case study in czech republic sector/traffic
  accidents,'' in {\em Second International Conference on Advanced Engineering
  Computing and Applications in Sciences} (C.~Dini, ed.), pp.~7--12, {IEEE}
  Computer Society, 2008.

\bibitem{dedek:DeEcExperimentswith2008}
J.~D{\v{e}}dek, A.~Eckhardt, and P.~Vojt{\'{a}}{\v{s}}, ``Experiments with
  czech linguistic data and {ILP},'' in {\em {ILP} 2008 (Late Breaking Papers)}
  (F.~{\v{Z}}elezn{\'{y}} and N.~Lavra{\v{c}}, eds.), (Prague, Czech Republic),
  pp.~20--25, Action M, 2008.

\bibitem{dedek:ReYaLiOntoText08}
M.~Reformat, R.~R. Yager, and Z.~Li, ``Ontology enhanced concept hierarchies
  for text identification,'' {\em Journal Semantic Web Information Systems},
  vol.~4, no.~3, pp.~16--43, 2008.

\bibitem{dedek:CAP}
M.~Chong, A.~Abraham, and M.~Paprzycki, ``Traffic accident analysis using
  machine learning paradigms,'' {\em Informatica}, vol.~29, pp.~89--98, 2005.

\bibitem{dedek:WebDataMining}
B.~Liu, {\em Web Data Mining}.
\newblock Springer-Verlag, 2007.

\bibitem{dedek:ZaPtTectoMTHighly2008}
Z.~{\v{Z}}abokrtsk{\'{y}}, J.~Pt{\'{a}}{\v{c}}ek, and P.~Pajas, ``Tecto{MT}:
  Highly modular {MT} system with tectogrammatics used as transfer layer,'' in
  {\em {ACL} 2008 {WMT}: Proceedings of the Third Workshop on Statistical
  Machine Translation}, (Columbus, {OH}, {USA}), pp.~167--170, Association for
  Computational Linguistics, 2008.

\bibitem{dedek:mcdonald}
R.~McDonald, F.~Pereira, K.~Ribarov, and J.~Hajic, ``Non-projective dependency
  parsing using spanning tree algorithms,'' in {\em Proceedings of Human
  Language Technology Conference and Conference on Empirical Methods in Natural
  Language Processing}, (Vancouver, British Columbia, Canada), pp.~523--530,
  Association for Computational Linguistics, October 2005.

\bibitem{dedek:staford_dependecies}
M.~C. de~Marneffe and C.~D. Manning, ``The {S}tanford typed dependencies
  representation,'' in {\em Coling 2008: Proceedings of the workshop on
  Cross-Framework and Cross-Domain Parser Evaluation}, (Manchester, UK),
  pp.~1--8, Coling 2008 Organizing Committee, August 2008.

\bibitem{dedek:GATE}
H.~Cunningham, D.~Maynard, K.~Bontcheva, and V.~Tablan, ``Gate: A framework and
  graphical development environment for robust nlp tools and applications,'' in
  {\em Proceedings of the 40th Annual Meeting of the ACL}, 2002.

\end{thebibliography}
